Reviving stochasticity: SMBH-binary eccentricity is inherently random

### 2023-06-06 papers/paper-eccentricity/paper-eccentricity.tex
Update GradientPlot classes to improve efficiency
- minor updates to paper plots

\begin{figure*}
    \includegraphics{eccentricities.pdf}
    \caption{Eccentricity $e$ (note the non-linear scale) as a function of shifted time $t'=t-t_\mathrm{bound}$ for select representative simulations from the $e_0 = 0.90$ set (blue lines) and $e_0 = 0.99$ set (orange lines). The downwards-pointing arrows indicate the mean time when the SMBH binaries becomes hard for the two simulation sets. In both the shown $e_0 = 0.90$ and $e_0 = 0.99$ sets, one simulation has a low eccentricity, displacing it to a value of $e$ greater than $2.5\sigma$ from the collective mean. In the $e_0=0.90$ set, two simulations have a SMBH binary merger, as indicated by the rapid circularisation of the eccentricity.}
    \label{fig:eccentricities}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{orbit}
    \caption{Orbits from $t=0\,\mathrm{Myr}$ to $t_\mathrm{bound}+\epsilon$ of a single SMBH in two representative realisations of the $e_0=0.90$ mergers (left) and the $e_0=0.99$ mergers (right), which by symmetry of the equal mass system is the same as the second BH orbit reflected. The term $\epsilon$ allows for the SMBH trajectory to be seen for some small time after the two SMBHs have become bound. Each line is coloured according to the shifted time $t'=t-t_\mathrm{bound}$ of the simulation, however the colours for $|t'|>2\,\mathrm{Myr}$ is constant for visual clarity of the later evolution. In each inset panel, point A shows a time just before the first hard scattering $\theta_\mathrm{defl}$, and point B a time just after. The circle marker indicates the final position of the SMBH before the SMBHs form a bound binary.}
    \label{fig:orbit}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics{eccentricities.pdf}
    \caption{Eccentricity $e$ (note the non-linear scale) as a function of shifted time $t'=t-t_\mathrm{bound}$ for select representative simulations from the $e_0 = 0.90$ set (blue lines) and $e_0 = 0.99$ set (orange lines). The downwards-pointing arrows indicate the mean time when the SMBH binaries becomes hard for the two simulation sets. In both the shown $e_0 = 0.90$ and $e_0 = 0.99$ sets, one simulation has a low eccentricity, displacing it to a value of $e$ greater than $2.5\sigma$ from the collective mean. In the $e_0=0.90$ set, two simulations have a SMBH binary merger, as indicated by the rapid circularisation of the eccentricity.}
    \label{fig:eccentricities}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{orbit}
    \caption{Orbits from $t=0\,\mathrm{Myr}$ to a time shortly after $t_\mathrm{bound}$ of a single SMBH in two representative realisations of the $e_0=0.90$ mergers (left) and the $e_0=0.99$ mergers (right), which by symmetry of the equal mass system is the same as the second BH orbit reflected. Each line is coloured according to the shifted time $t'=t-t_\mathrm{bound}$ of the simulation, however the colours for $|t'|>2\,\mathrm{Myr}$ is constant for visual clarity of the deflection-phase of the evolution. In each inset panel, point A shows a time just before the first hard scattering $\theta_\mathrm{defl}$, and point B a time just after. The circle marker indicates the position of the SMBH just before the SMBHs form a bound binary.}
    \label{fig:orbit}
\end{figure*}
